Figures to insert in text

### 2018-03-05 Chapters/Chapter02.tex
SDM

As predicted by Kanerva, the distance between two bitstrings follows a binomial distribution with mean $\mu = n/2$ and standard deviation $\sigma = \sqrt{n}/2$. For large values of $n$, it may be approximated by a normal distribution with the same mean and standard deviation.

In order to validate our random bitstring generation algorithm, we have calculated 10,000 distances between two random bitstrings with 1,000 bits. In total, 20,000 bitstrings have been generated. The code is available in the ``Distance between bitstrings'' notebook.

@@

\begin{figure}[h!]
  \centering
  \subfloat[Full histogram ]{\includegraphics[width=0.5\textwidth]{./images02/new-images/bs-hist-full.png}}
  \subfloat[{Zoom in the interval $[400, 600]$} ]{\includegraphics[width=0.5\textwidth]{./images02/new-images/bs-hist-zoom.png}}

>>>>

As showed by \citet{Kanerva1988}, the distance between two bitstrings follows a binomial distribution with mean $\mu = n/2$ and standard deviation $\sigma = \sqrt{n}/2$. For large values of $n$, it may be approximated by a normal distribution with the same mean and standard deviation.

In order to validate our random bitstring generation algorithm, we have calculated 10,000 distances between two random bitstrings with $n=1,000$ bits. In total, 20,000 random bitstrings have been generated during the simulation. The code is available in the ``Distance between bitstrings'' notebook \citep{sdmframework}.

@@

This also validates the algorithm used to calculate the distance between two bitstrings. In this simulation, we have used the built-in \_\_popcnt() function.

\begin{figure}[!htb]
  \centering
  \subfloat[Full histogram ]{\includegraphics[width=0.5\textwidth]{./images02/new-images/bs-hist-full.png}}
  \subfloat[{Zoom in the interval $[400, 600]$} ]{\includegraphics[width=0.5\textwidth]{./images02/new-images/bs-hist-zoom.png}}
